Preregistration analysis, Cost 2 study

### 2019-05-14 Cost2/Cost2_prereg.Rmd
forced travel plots ready

# forced travels as a function of time
# number of forced travels as a function of time for cognitive and grip trials
forcedTravels <- dataAll %>%
  filter(rawChoice == 2) %>%
  group_by(SubjID, Cost, Block) %>%
  count() %>%
  group_by(Cost, Block) %>%
  summarise(mTravels = mean(n),
            SE = sd(n) / sqrt(21))

@@

  ggplot(data = forcedTravels, aes(Block, mTravels, color = Cost )) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = mTravels - SE, ymax = mTravels + SE), width = 0.4) +
    scale_x_continuous(breaks = seq(6)) +
    labs(y = "Mean n of forced travels") +
    ylim(0, 4) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))
```

>>>>

# forced travels as a function of time
# number of forced travels as a function of time for cognitive and grip trials
forcedTravels <- dataAll %>%
  #filter(rawChoice == 2) %>%
  group_by(SubjID, Cost, Block) %>%
  filter(Cost %in% c("Cognitive", "Physical")) %>%
  summarise(pTravel = mean(rawChoice == 2)) %>%
  group_by(Cost, Block) %>%
  summarise(mTravels = mean(pTravel),
            SE = sd(pTravel) / sqrt(21))

@@

ggplot(data = forcedTravels, aes(Block, mTravels, color = Cost )) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mTravels - SE, ymax = mTravels + SE), width = 0.4) +
  scale_x_continuous(breaks = seq(6)) +
  labs(y = "Prop. of forced travels") +
  ylim(0, NA) +
  theme(legend.key = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))
```
